---
title: "Report title"
author: "Your name"
date: "Today's date"
output:
  html_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(gridExtra)
library(readr)
library(RSQLite)

knitr::opts_chunk$set(echo=FALSE, fig.width=10, message=FALSE, warning=FALSE, fig.height=4)

conn = DBI::dbConnect(SQLite(), "summary.sqlite3")
summary = tbl(conn, "summary") %>% collect
per_user = tbl(conn, "per_user_daily_averages") %>% collect
```

# Executive summary

<!--
Consider including:
 * A summary of results
 * Links to the PHD and any relevant bugs
-->

# Introduction

<!--
Consider including:
 * Any useful background on the experiment you ran and why you expected it to be interesting
 * Links to any requirements documents
-->

# Results

## Experiment-specific outcome measures

<!--
Present results here.

Consider rewording the headers to summarize the contents of the section
(e.g. instead of "Total time per user", try "Total time per user was similar" or
"Total time per user increased 30%")
-->

## Engagement

### Total time per user

```{r total_time_per_user}
densityplot = ggplot(per_user, aes(subsession_length/3600, color=experiment_branch)) +
  geom_density() +
  scale_x_log10() +
  scale_color_discrete("Branch") +
  labs(x="Daily session lengths on active days (hours)")

summaryplot = summary %>%
  filter(metric_name == "engagement_avg_daily_hours", stat_name == "p50") %>%
  ggplot(aes(branch, stat_value, ymin=ci_low, ymax=ci_high)) +
    geom_pointrange() +
    labs(x="Branch", y="Median daily session length")

grid.arrange(densityplot, summaryplot, ncol=2)
```

Median daily session length (on days when users used the browser at all).

### Active time per user
```{r active_time_per_user}
densityplot = ggplot(per_user, aes(active_ticks*5/3600, color=experiment_branch)) +
  geom_density() +
  scale_x_log10() +
  scale_color_discrete("Branch") +
  labs(x="Daily active time per user on active days (hours)")

summaryplot = summary %>%
  filter(metric_name == "engagement_avg_daily_active_hours", stat_name == "p50") %>%
  ggplot(aes(branch, stat_value, ymin=ci_low, ymax=ci_high)) +
    geom_pointrange() +
    labs(x="Branch", y="Median daily active time (hours)")

grid.arrange(densityplot, summaryplot, ncol=2)
```


### Session intensity

```{r intensity_density}
densityplot = ggplot(per_user, aes(active_ticks*5/subsession_length, color=experiment_branch)) +
  geom_density(n=8192) +
  scale_color_discrete("Branch") +
  labs(x="Daily intensity on active days (fraction)") +
  coord_cartesian(xlim=c(0, 1))

summaryplot = summary %>%
  filter(metric_name == "engagement_intensity", stat_name == "p50") %>%
  ggplot(aes(branch, stat_value, ymin=ci_low, ymax=ci_high)) +
    geom_pointrange() +
    labs(x="Branch", y="Median daily session intensity (fraction)")

grid.arrange(densityplot, summaryplot, ncol=2)
```

### URIs visited per active hour

```{r uris_active_hour}
densityplot = ggplot(per_user, aes(scalar_parent_browser_engagement_total_uri_count/(active_ticks*5/3600), color=experiment_branch)) +
  geom_density() +
  scale_color_discrete("Branch") +
  scale_x_log10() +
  labs(x="URIs visited per active hour")

summaryplot = summary %>%
  filter(metric_name == "engagement_uris_per_active_hour", stat_name == "p50") %>%
  ggplot(aes(branch, stat_value, ymin=ci_low, ymax=ci_high)) +
    geom_pointrange() +
    labs(x="Branch", y="URIs visited per active hour")

grid.arrange(densityplot, summaryplot, ncol=2)
```

## Retention

### 3-week retention

### Active 3-week retention

# Discussion

<!--
Discuss and contextualize the results here.
-->

# Methods

mozreport was version MOZREPORT_VERSION.
